Analytic Doppler Imaging

### 2019-08-20 tex/ms.tex
fixing blas

@@

    $J$                      & \# of spectral components                             & \\
    $K$                      & \# of wavelength bins in the observed spectrum        & \\
    $K'$                     & \# of wavelength bins in the latent spectrum          & \\
    $M$                      & \# of epochs observed                                 & \\
    $N$                      & \# of spherical harmonic coefficients                 & \\
    $N'$                     & \# of spherical harmonic coefficients after limb darkening            & \\
    $W$                      & \# of wavelength bins in the convolution kernel       & \\

@@

@@

>>>>

\begin{figure}[p!]
    \begin{centering}
    \oscaption{spotstar}{%
        \xxx{Figure here with the problem setup.}
        \label{fig:spotstar}
    }
    \end{centering}
\end{figure}

@@

    $J$                      & \# of spectral components                             & \S\ref{sec:eigen} \\
    $K$                      & \# of wavelength bins in the observed spectrum        & \S\ref{sec:linear} \\
    $K'$                     & \# of wavelength bins in the latent spectrum          & \S\ref{sec:linear}\\
    $M$                      & \# of epochs observed                                 & \S\ref{sec:linear}\\
    $N$                      & \# of spherical harmonic coefficients                 & \S\ref{sec:linear}\\
    $N'$                     & \# of spherical harmonic coefficients after limb darkening & \S\ref{sec:ld}\\
    $W$                      & \# of wavelength bins in the convolution kernel       & \S\ref{sec:linear}\\

@@

    $\boldsymbol{\mathbb{S}}$& matrix of $J$ spectral components                     & Equation~(\ref{eq:eigen:azero})\\

@@

    $\boldsymbol{\mathbb{Y}}$& matrix of $J$ spherical harmonic components           & Equation~(\ref{eq:eigen:azero})\\
